### 2011-11-07 doc/pldi2012/highlevel.tex
spell check

The high-level runtime also supports the use of multiple mappers in the same application.  Each task 
call may (but does not need to) have an associated mapper,
%runtime  can choose a mapper to be used for the runtime calls made inside that
%task.  
which allows for the creation of library code that provides its own mappers indpendent
from any application level mappers.

@@

\subsection{Execution}
\label{subsec:execution}
Once task mapping is complete the high-level runtime performs the necessary operations
to issue the task to the low level runtime.  It first creates any new physical instances
for the regions the task requires.  It then issues copy operations required
for the task to execute contignent on predecessor tasks producing the source physical instances
having finished.  Then it issues the task itself to the low level processor contingent
on all the copies for the task haveing finished as well as the the set of tasks
on which the issuing task depends having finished.  These dependences are all encoded
using {\em events} (see Section \ref{subsec:events}).  Continuing the analogy of an out-of-order
processor, the execution phase is equivalent to issuing an instruction to an
execution unit, and having the execution unit defer the instruction's execution until all its
operands are ready.  The low-level runtime contains processors that act as execution
units that will run a task once all of the events required for the task to run
have occurred.

@@

The last part of the completetion phase is garbage collecting physical instances.  Physical
instances are not a visible part of the programming model and therefore cannot be managed
directly by the programmer.  Having the mapper manage them would introduce correctness
issues.  We use a two-level reference counting scheme on both abstract instances and physical
instances to know when it is safe to reclaim physical instances.  Due to space constraints
we omit the details of this algorithm.

>>>>

The high-level runtime also supports the use of multiple mappers in the same application.  Each task 
call may (but does not need to) have an associated mapper,
%runtime  can choose a mapper to be used for the runtime calls made inside that
%task.  
which allows for the creation of library code that provides its own mappers ind pendent
from any application level mappers.

@@

\subsection{Execution}
\label{subsec:execution}
Once task mapping is complete the high-level runtime performs the necessary operations
to issue the task to the low level runtime.  It first creates any new physical instances
for the regions the task requires.  It then issues copy operations required
for the task to execute contingent on predecessor tasks producing the source physical instances
having finished.  Then it issues the task itself to the low level processor contingent
on all the copies for the task having finished as well as the the set of tasks
on which the issuing task depends having finished.  These dependences are all encoded
using {\em events} (see Section \ref{subsec:events}).  Continuing the analogy of an out-of-order
processor, the execution phase is equivalent to issuing an instruction to an
execution unit, and having the execution unit defer the instruction's execution until all its
operands are ready.  The low-level runtime contains processors that act as execution
units that will run a task once all of the events required for the task to run
have occurred.

@@

The last part of the completion phase is garbage collecting physical instances.  Physical
instances are not a visible part of the programming model and therefore cannot be managed
directly by the programmer.  Having the mapper manage them would introduce correctness
issues.  We use a two-level reference counting scheme on both abstract instances and physical
instances to know when it is safe to reclaim physical instances.  Due to space constraints
we omit the details of this algorithm.
